Methods for Polyphonic Music Transcription

### 2013-12-01 paper/paper.tex
Added introduction, terminology, motivation, and some methodologies like NMF

% State the problem
We present a review of modern methods for polyphonic music transcription.

@@

@@

@@

>>>>

% State the problem
%We present a review of modern methods for polyphonic music transcription.

Music transcription is the process of converting an audio recording into a musical score. 
Musicians have been transcribing music manually for centuries to learn new songs and gain musical insight.
Transcription, however, is an arduous manual process for musicians, and it's a difficult problem for computers because the pitches in a musical score are the human perceptions of a time-varying and frequency-varying physical phenomenon. 
There has been a flurry of research on how to solve this problem. 
We investigate the best solutions to the automated transcription problem and evaluate and compare their performance.

@@

Polyphony means multiple simultaneous notes. Monophony means only a single note at a time. These terms carry slightly different meanings outside of the automated transcription field.

@@

% Introduction

% Explain motivation

% This is just copied from 'A Connectionist Approach to Automatic Transcription of Polyphonic Piano Music' for now:
Applications of a music transcription are versatile. Transcription produces a compact and standardized parametric representation of music. Such representation is needed for content-based retrieval of music in most current musical databases. It is useful in music analysis systems for tasks such as melody extraction, music segmentation and rhythm tracking. Transcription aids musicologists in analyzing music that has never been written down, such as improvised or ethnical music. The conversion of an acoustical waveform into parametric description is also useful in the process of making music, as well as in newer coding standards, such as MPEG-4, which may include such descriptions.

@@

Non-negative matrix factorization (NMF) is an unsupervised, dimensionality reduction technique that factors a non-negative matrix $V$ with dimensions $FxN$ into two matrices,

\[ V \approx WH \]

\noindent where $W$ is an $FxK$ matrix and $H$ is a $KxN$ matrix. $K$ is typically chosen so that $F*K + K*N << F*N$.

In piano transcription, for example, $V$ might be a spectrogram with dimensions $2048xN$, $W$ might be $2048x88$ and encode the spectral envelope for each piano key in each column of the matrix, and $H$ might be $88xN$ sparse piano roll matrix.

There are two cost functions commonly used for NMF. The first is a euclidean distance cost function, defined as the squared difference between the corresponding elements in each matrix:

\[ \displaystyle ||V-WH||^{2} = \sum_{ij} (V_{ij} - (WH)_{ij})^{2} \]

\noindent Another commonly used measure is the KL divergence:

\[ \displaystyle D(V||WH) = \sum_{ij} (V_{ij} \log \frac{V_{ij}}{(WH)_{ij}} - V_{ij} + (WH)_{ij}) \]

The KL divergence cost function is more often used by transcription researchers because it XXX.
